---
title: "Final assessment"
author: "Ayoub Yousssoufi"
date: "12/4/2021"
output: html_document
---

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Large data processing with R 

This is the final exam in R. You will find in this markdown my report related to the exam 1

```{r package , echo= FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(corrplot)
library(gridExtra)

```
**1. Getting to know the data**                                                             
 <u> Column names & Dimension </u>

```{r csvfile , echo= FALSE, message=FALSE}

data <- read.csv("movies.csv")
#View(data)
colnames(data)
dim(data)

```
**2.	Scatterplots**</br>
a.	do scatter plot of Tickets Sold and Gross 
```{r scatter, echo=FALSE, message=FALSE}
p <- data %>% ggplot() +geom_point(aes(x =Tickets_Sold , y =Gross_Sales), size = 3)+xlab("Tickets sold") + ylab("Gross Sales") 
p
```

b.	What is the correlation between tickets sold and sales? Is this expected?
```{r corr, echo=FALSE, message=FALSE}
cor(x =data$Tickets_Sold , y =data$Gross_Sales)
```
**3.	Other plots**
a.	do boxplot
```{r boxplot, echo=FALSE, message=FALSE}
ggplot(data) + geom_boxplot(aes(x =Tickets_Sold , y =Gross_Sales), fill = 'lightblue')
```

b.	do histogram for type of films

```{r histogram, echo=FALSE, message=FALSE}
count <- data  %>% group_by(Genre) %>% count()
count <- count %>% rename("movie_count"=n)
ggplot(count) + geom_histogram(aes(x=Genre, y=movie_count), stat="identity")+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

c.	do histogram of ticket sales. Try different bin numbers
```{r plot1, echo=FALSE, message=FALSE}

ggplot(data) + geom_histogram(aes(Tickets_Sold),bins = 20, color='blue', fill='black')

```

The same question with different bins.
```{r plot2, echo=FALSE, message=FALSE}

ggplot(data) + geom_histogram(aes(Tickets_Sold),bins = 50, color='blue', fill='black')

```

d.	Add frequency count to top of bars. 
```{r plotFrequency, echo=FALSE, message=FALSE}
data$convert <- NA
for(i in 1:length(data$Tickets_Sold)){
  
  data$convert[i] <-data$Tickets_Sold[i]/10**6
}
hist(data$convert,labels = TRUE, xlab ='Tickets Sold',main =paste("Frequency of ticket sold 10^-6"), col = 'red') 

```


e.	do barplot of genre
```{r plot_bar, echo=FALSE, message=FALSE}

ggplot(data) + geom_bar(aes(Genre),bins = 10)+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

4.	Create a set of functions that compute specific metrics by genre:
```{r mean, echo=FALSE, message=FALSE}

avg_calcul <- function(x,y){
  aggregate(x ~ y, data , mean)
}
avg_calcul(data$Tickets_Sold,data$Genre)
avg_calcul(data$Gross_Sales,data$Genre)

```

5.	Use the functions created in 4 to compute these metrics by distributor.

```{r distributor, echo=FALSE, message=FALSE}

avg_calcul(data$Tickets_Sold,data$Distributor)
avg_calcul(data$Gross_Sales,data$Distributor)

```
## Winter Olympic
```{r winter olympic, echo=FALSE, message=FALSE}
library(dplyr)
data_dfw <- read.csv("winter_olympic.csv")
```
1.	Getting to know the data:
```{r winter data, echo=FALSE, message=FALSE, }
#View(data_dfw)
colnames(data_dfw)
dim(data_dfw)

```
2.	Data is currently sorted by Rank. Sort data by total medals and country. Assign sorted data to a new data frame. 
```{r data sort , echo=FALSE, message=FALSE, }

sort_total<- data_dfw[order(-data_dfw$Total),]
head(sort_total)
```
3.	Use some function to look at data.
```{r data_explore , echo=FALSE, message=FALSE, }
l1 <- aggregate(data_dfw$Total, by=list(data_dfw$Region), FUN=sum)# number of medals won/ country, Europe won the most
lg <- aggregate(data_dfw$Gold, by=list(data_dfw$Region), FUN=sum) #Europe leading in the gold medals
ls <- aggregate(data_dfw$Silver, by=list(data_dfw$Region), FUN=sum)# Europe leading in the silver
lb <- aggregate(data_dfw$Bronze, by=list(data_dfw$Region), FUN=sum)
l1
lg
ls
```
4.	Look at some statistics
```{r data stat , echo=FALSE, message=FALSE, }
apply(data_dfw[,3:6], 2, sum)
aggregate(.~NOC, data_dfw[,2:ncol(data_dfw)-2], FUN = function(x) sum(x==0))

```
look at the mean and total number of G, S, B and T medals
```{r data_analysis , echo=TRUE, message=FALSE, }
apply(data_dfw[,3:6], 2, median)
apply(data_dfw[,3:6], 2, mean)

```
6.	More statistics - subset
```{r data_analysis2 , echo=TRUE, message=FALSE, }
aggregate(.~Region, data_dfw[,3:ncol(data_dfw)], FUN = median)
aggregate(.~Region, data_dfw[,3:ncol(data_dfw)], FUN = mean) 

```
c.	How many countries are in this Geographic Region?
```{r data_analysis3 , echo=TRUE, message=FALSE, }
length(data_dfw[data_dfw$Region=="NORTH_A"]) 
```
d.	How many countries are in the EUROPE group?
```{r data_analysis4 , echo=TRUE, message=FALSE, }
nrow(subset(data_dfw, data_dfw$Region =="EUROPE"))

```
e.	What is the max number of medals won? 
```{r data_analysis5 , echo=TRUE, message=FALSE, }

aggregate(.~Region, data_dfw[,3:ncol(data_dfw)], FUN = max)

```
What country won the max?
Russia has won most the medal during the competition
```{r data_analysis6 , echo=TRUE, message=FALSE, }

result<- aggregate(.~NOC, data_dfw[,2:ncol(data_dfw)], FUN = max)
result1 <- transform(result, Total = as.numeric(Total))
result[order(result1$Total, decreasing = TRUE),]
```
## Summer-winter Olympic
1.	Dealing with Data
```{r summer_winter_olympic, echo=FALSE, message=FALSE}
library(dplyr)
data_df <- read.csv("summer_winter_olympics.csv")
names(data_df) <- c('countryID','country', 'number_summer_played', 'gold_s', 'silver_s', 'bronze_s', 'total_summer',
                         'number_winter_played','gold_w','silver_w','bronze_w','total_winter','Total_games',
                    'total_gold','total_silver','total_bronze','total_year')
head(data_df)
```
c.	use table() to find frequency of total summer games played
```{r table_analysis, echo=FALSE, message=FALSE}
table(data_df$number_summer_played)
```
d.	explore the data with other variables
```{r table_explore, echo=FALSE, message=FALSE}
table(data_df$gold_s)
```
4.	Graphs
a.	do histogram of summer games (total)
```{r hist1, echo=FALSE, message=FALSE}
p2 <- ggplot(data_df) + geom_histogram(aes(x=number_summer_played, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = number_summer_played),col = 'green')
p2
```
b.	do histogram of winter games (total)
```{r hist2, echo=FALSE, message=FALSE}
p3 <- ggplot(data_df) + geom_histogram(aes(x=number_winter_played, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = number_winter_played),col = 'green')
p3
```
c.	put above two histograms on one page
```{r subplot1, echo=FALSE, message=FALSE}
grid.arrange(p2,p3,ncol=2) 
```
d.	do two histograms on one page: total summer, total winter medals won
```{r subplot2, echo=FALSE, message=FALSE}
ggplot(data_df)+geom_histogram(aes(x=total_summer,fill='total summer'))+
  geom_histogram(aes(x=total_winter,fill='total winter'))
```
e.	is there a correlation between number of medals given out in winter and summer? (do plot)
```{r correlation1, echo=FALSE, message=FALSE}
data_df.cor = cor(data_df[,3:ncol(data_df)], method = c("spearman"))
palette = colorRampPalette(c("green", "white", "red")) (20)
heatmap(x = data_df.cor, col = palette, symm = TRUE)
cor(x =data_df$total_winter , y =data_df$total_summer)
```
f.	how about number of games each country competes in. Is there correlation between winter and summer?
```{r correlation2, echo=FALSE, message=FALSE}
cor(x =data_df$number_winter_played , y =data_df$number_summer_played)
```
g.	look at distribution of each of the types of medals, by season (6 histograms on one page)
```{r histSub, echo=FALSE, message=FALSE}
d1 <- ggplot(data_df) + geom_histogram(aes(x=gold_s, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = gold_s),col = 'black') 
d2 <- ggplot(data_df) + geom_histogram(aes(x=silver_s, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = silver_s),col = 'black') 
d3 <- ggplot(data_df) + geom_histogram(aes(x=bronze_s, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = silver_s),col = 'black') 
d4 <- ggplot(data_df) + geom_histogram(aes(x=gold_w, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = silver_s),col = 'black') 
d5 <- ggplot(data_df) + geom_histogram(aes(x=silver_w, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = silver_s),col = 'black') 
d6 <- ggplot(data_df) + geom_histogram(aes(x=bronze_w, y=..density..), bins=25,fill='blue')+
  geom_density(aes(x = silver_s),col = 'black') 

grid.arrange(d1, d2, d3, d4,d5,d6, ncol=3, nrow = 2)
```
h.	redo g with different number of bins (10 instead of 20)
```{r binschanges, echo=FALSE, message=FALSE}
bins <- function(b){
  
  d1 <- ggplot(data_df) + geom_histogram(aes(x=gold_s, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = gold_s),col = 'black') 
  d2 <- ggplot(data_df) + geom_histogram(aes(x=silver_s, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = silver_s),col = 'black') 
  d3 <- ggplot(data_df) + geom_histogram(aes(x=bronze_s, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = silver_s),col = 'black') 
  d4 <- ggplot(data_df) + geom_histogram(aes(x=gold_w, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = silver_s),col = 'black') 
  d5 <- ggplot(data_df) + geom_histogram(aes(x=silver_w, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = silver_s),col = 'black') 
  d6 <- ggplot(data_df) + geom_histogram(aes(x=bronze_w, y=..density..), bins=b,fill='blue')+
    geom_density(aes(x = silver_s),col = 'black') 
  
 return(grid.arrange(d1, d2, d3, d4,d5,d6, ncol=3, nrow = 2))
}
bins(10)
```





